{\it Proposal:}\\ Determining the efficacy of pulsed microwave-acoustic viral envelope disruption in COVID-19 treatment

### 2020-08-20 documents/clinical_protocol.tex
Protocol

@@

@@

Since the genitals are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.

>>>>

In female patients, much of the lung is shielded by breast tissues. However, since fat is not particularly conductive,

@@

preliminary

@@

Since the reproductive organs are not involved in the infection; and they will not receive a dose above background.\cite{Organ2004}.
